Covariate analysis of UFL-Mayo-ISB RNASeq reprocessed counts (both cerebellum and temporal cortex)

### 2016-07-13 code/Rmd/Mayo_RNASeq_Reprocessed.Rmd
Added PMI data to SVA based adjustments with Mayo reprocessed counts

VOOM.ADJUSTED.GENE_EXPRESSION$E <- rownameToFirstColumn(VOOM.ADJUSTED.GENE_EXPRESSION$E, 'Gene.ID') %>%
  left_join(backgroundGenes) %>% left_join(Ensemble2HGNC) %>%
  dplyr::select(Gene.ID, ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))
```
### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=25, fig.width=25}
# Fit contrast
contrast = makeContrasts(contrasts=c(
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.Pathologic_Aging",
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.PSP",
  "BrainRegion.DiagnosisCER.Pathologic_Aging-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.PSP-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.Pathologic_Aging-BrainRegion.DiagnosisCER.PSP",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.Pathologic_Aging",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.PSP",
  "BrainRegion.DiagnosisTCX.Pathologic_Aging-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.PSP-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.Pathologic_Aging-BrainRegion.DiagnosisTCX.PSP"), 
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)

>>>>

VOOM.ADJUSTED.GENE_EXPRESSION$E <- rownameToFirstColumn(VOOM.ADJUSTED.GENE_EXPRESSION$E, 'Gene.ID') %>%
  left_join(backgroundGenes) %>% left_join(Ensemble2HGNC) %>%
  dplyr::select(Gene.ID, ensembl_gene_id, hgnc_symbol, one_of(rownames(COVARIATES)))
```
### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=10, fig.width=20}
# Fit contrast
contrast = makeContrasts(contrasts=c(
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.Pathologic_Aging",
  "BrainRegion.DiagnosisCER.Control-BrainRegion.DiagnosisCER.PSP",
  "BrainRegion.DiagnosisCER.Pathologic_Aging-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.PSP-BrainRegion.DiagnosisCER.AD",
  "BrainRegion.DiagnosisCER.Pathologic_Aging-BrainRegion.DiagnosisCER.PSP",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.Pathologic_Aging",
  "BrainRegion.DiagnosisTCX.Control-BrainRegion.DiagnosisTCX.PSP",
  "BrainRegion.DiagnosisTCX.Pathologic_Aging-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.PSP-BrainRegion.DiagnosisTCX.AD",
  "BrainRegion.DiagnosisTCX.Pathologic_Aging-BrainRegion.DiagnosisTCX.PSP"), 
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)
